Accurate Description of Cation Binding to Lipid Bilayers with Negatively Charged Phosphatidylserine Requires Accounting for Electronic Polarization

### 2019-07-12 Manuscript/manuscript.tex
Improvements in abstract +1 todo

\begin{abstract} 
  Phosphatidylserine (PS) lipids are important signaling molecules and the most common negatively charged lipids in eukaryotic membranes.
  The signaling can be often regulated with calcium, but its interactions with PS headgroups are not fully understood.
  Classical molecular dynamics (MD) simulations can potentially give detailed description of lipid-ion interactions,
  but the results strongly depend on the used force field.
  Here, we apply the electronic continuum correction (ECC) to the Amber Lipid17 parameters of POPS lipid to improve its
  interactions with Na$^+$ and Ca$^{2+}$ ions.
  The partial charges of headgroup, glycerol backbone and carbonyls of POPS, bearing a unit negative charge, were scaled with a
  factor of 0.75, derived for monovalent ions and the Lennard-Jones $\sigma$ parameters of the same segments were scaled with a factor of 0.89.
  The resulting ECC-POPS models, gives more realistic interactions with Na$^+$ and Ca$^{2+}$ cations than the original Amber Lipid17 parameters,
  when validated using the headgroup order parameters and ''electrometer concept''.
  In ECC-lipids simulations, the Ca$^{2+}$ cations do not simultaneously interact with more than two PS lipids, and interactions 
  carboxylate groups is twice more likely than with phosphate group, while interaction with carbonyls is almost negligible.
  Our results pave the way for more realistic MD simulations of anionic biological membranes and demonstrate the ECC
  approach is useful also for charged lipids.
\end{abstract}

>>>>

\begin{abstract} 
  Phosphatidylserine (PS) lipids are important signaling molecules and the most common negatively charged lipids in eukaryotic membranes.
  The signaling can be often regulated by calcium, but its interactions with PS headgroups are not fully understood.
  \todo{The way we write "head groups" resp. "headgroups" has to be united. 
        I prefer "head groups" as it is gramatically correct, but I am fine with either of the options.}
  Classical molecular dynamics (MD) simulations can potentially give detailed description of lipid-ion interactions,
  but the results strongly depend on the used force field.
  Here, we apply the electronic continuum correction (ECC) to the Amber Lipid17 parameters of POPS lipid to improve its
  interactions with Na$^+$ and Ca$^{2+}$ ions.
  The partial charges of headgroup, glycerol backbone and carbonyls of POPS, bearing a unit negative charge, were scaled with a
  factor of 0.75, derived for monovalent ions and the Lennard-Jones $\sigma$ parameters of the same segments were scaled with a factor of 0.89.
  The resulting ECC-POPS models, gives more realistic interactions with Na$^+$ and Ca$^{2+}$ cations than the original Amber Lipid17 parameters,
  when validated using headgroup order parameters and ''electrometer concept''.
  In ECC-lipids simulations, Ca$^{2+}$ cations do not simultaneously interact with more than two PS lipids, and interactions 
  with carboxylate groups is twice more likely than with phosphate groups, while interaction with carbonyls is almost negligible.
  Our results pave the way for more realistic MD simulations of anionic biological membranes and demonstrate the 
  usefulness of ECC also to charged lipids.
\end{abstract}
